SMT-Boosted Security Types for Low-Level MPC

### 2025-06-10 esop25/sharety.tex
checkpoint

  \inferrule[Defn]
      {e_1 \redx \mx{w}{\cid_1} \\ e_2 \redx \elab{\be}{\cid_2}}
      {\shtrip{\Gamma, R, \xdefs}{e_1 := e_2}{\Gamma, R, \xdefs[\mx{w}{\cid_1} \mapsto \toeq{\elab{\be}{\cid_2}}]}}
\end{mathpar}
The remaining rules are as follows, where ``evaluating substitution''
$\redxsub(\notg{R}),\redxsub(\notg{\Gamma})$ is defined to impose evaluation
\cnote{probably should do this for $\peq$ as well}. I.e., given $\redxsub = [e_1/y_1 \cdots e_n/y_n]$:
    $$
    \redxsub(\notg{\Gamma}) = \Gamma \ \text{where}\ \notg{\Gamma}[e_1/y_1 \cdots e_n/y_n] \redx \Gamma
    $$
and so on.:
\begin{mathpar}
  \inferrule[App]
      {f : \Pi y_1,\ldots,y_n. \notg{\Gamma_1} \rightarrow (\notg{R'},\notg{\Gamma_2}) \\
       \redxsub = [e_1/y_1 \cdots e_n/y_n]}
      {\shtrip{\Gamma;\redxsub(\notg{\Gamma_1}), R, \xdefs}{f(e_1,\ldots,e_n)}{\Gamma;\redxsub(\notg{\Gamma_2}), R;\redxsub(\notg{R'}), \xdefs}}

>>>>

  \inferrule[Defn]
      {e_1 \redx \mx{w}{\cid_1} \\ e_2 \redx \elab{\be}{\cid_2}}
      {\shtrip{\Gamma, R, \xdefs}{e_1 := e_2}{\Gamma, R, \xdefs[\mx{w}{\cid_1} \mapsto \toeq{\elab{\be}{\cid_2}}]}}
\end{mathpar}
The remaining rules are as follows, with the rule for application
being the most interesting as usual. Since we allow dependent
generalization in function types, as in previous work (and as in the
Hoare logic) we equate expressions up to the result of their
evaluation. To make rules a little more succint we define ``evaluating
substitution'' $\redxsub(\notg{R}),\redxsub(\notg{\Gamma})$ to also
impose evaluation \cnote{probably should do this for $\peq$ as
  well}. I.e., given $\redxsub = [e_1/y_1 \cdots e_n/y_n]$:
    $$
    \redxsub(\notg{\Gamma}) = \Gamma \ \text{where}\ \notg{\Gamma}[e_1/y_1 \cdots e_n/y_n] \redx \Gamma
    $$
and so on.:
\begin{mathpar}
  \inferrule[App]
      {f : \Pi y_1,\ldots,y_n. \notg{\Gamma_1} \rightarrow (\notg{R'},\notg{\Gamma_2}) \\
       \redxsub = [e_1/y_1 \cdots e_n/y_n]}
      {\shtrip{\Gamma;\redxsub(\notg{\Gamma_1}), R, \xdefs}{f(e_1,\ldots,e_n)}{\Gamma;\redxsub(\notg{\Gamma_2}), R;\redxsub(\notg{R'}), \xdefs}}
